What do incoming university students believe about open science practices in

### 2022-03-21 analysis/Manuscript.Rmd
create Table 2 with metadata

```{r normsinpracticeitems}
practice_items = data.frame(
  "Practice" = c("Preregistration", "Registered Reports", "p-hacking", "HARKing", "Information for replicability",
                 "Preprints", "Open materials", "Open data", "Data on request", "Open access"),
  "Item" = c("The plan for collecting and analysing data for the study is posted in an online registry before data collection starts",
             "A plan for the study is submitted to a journal to be checked by experts (peer reviewed) before the data is collected and analysed",
             "The researchers run many different analyses of the data, and report only those that produce interesting findings",
             "The researchers describe their results as if they predicted those results from the beginning, even if that isn’t actually true",
             "The researchers provide enough practical detail in their written report that another researcher could fully repeat (replicate) their study without needing to ask any questions of the original researchers",
             "A manuscript describing the findings of the study is posted openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal",
             "The written materials and measures for the study are posted openly online so that other researchers and members of the public can access and use them",
             "Once the study is published, the anonymous responses from participants are posted openly online so that anyone can access and use the responses in their own research",
             "Once the study is published, the anonymous responses from participants are available to other researchers on request",
             "The research report describing the study and its findings is published in a journal that is free for anyone to access")
)

@@

@@

Participants who indicated they had heard of the replication crisis were asked, "What do you think 'the replication crisis' is"? Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most (`r sum(crisis_descriptions$Accurate =="y")/length(df$crisis_text[is.na(df$crisis_text)==FALSE])*100`%) provided responses consistent with the conventional interpretation of the term (i.e., describing a realisation that some or many scientific findings cannot be replicated). Example responses included, "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated". Only `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").

>>>>

```{r normsinpracticeitemsold, eval = FALSE}
practice_items = data.frame(
  "Practice" = c("Preregistration", "Registered Reports", "p-hacking", "HARKing", "Information for replicability",
                 "Preprints", "Open materials", "Open data", "Data on request", "Open access"),
  "Item" = c("The plan for collecting and analysing data for the study is posted in an online registry before data collection starts",
             "A plan for the study is submitted to a journal to be checked by experts (peer reviewed) before the data is collected and analysed",
             "The researchers run many different analyses of the data, and report only those that produce interesting findings",
             "The researchers describe their results as if they predicted those results from the beginning, even if that isn’t actually true",
             "The researchers provide enough practical detail in their written report that another researcher could fully repeat (replicate) their study without needing to ask any questions of the original researchers",
             "A manuscript describing the findings of the study is posted openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal",
             "The written materials and measures for the study are posted openly online so that other researchers and members of the public can access and use them",
             "Once the study is published, the anonymous responses from participants are posted openly online so that anyone can access and use the responses in their own research",
             "Once the study is published, the anonymous responses from participants are available to other researchers on request",
             "The research report describing the study and its findings is published in a journal that is free for anyone to access")
)

@@

```{r normsinpracticeitems}

# create a table with the norms in practice items from the metadata

practice_items <- metadata %>% 
  filter(scale == "practice") %>% 
  select (c(text_label, item_text))

knitr::kable(practice_items,
             caption = "Norms in practice items",
             col.names = c("Practice", "Item"),
             align = c('ll'))

```
\

@@

Participants who indicated they had heard of the replication crisis were asked, "What do you think 'the replication crisis' is"? Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most (`r sum(crisis_descriptions$accurate =="y")/length(df$crisis_text[is.na(df$crisis_text)==FALSE])*100`%) provided responses consistent with the conventional interpretation of the term (i.e., describing a realisation that some or many scientific findings cannot be replicated). Example responses included, "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated". Only `r sum(crisis_descriptions$accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").
